Locating Data Flow Anomaly With Statistical Distance

### 2017-09-07 Paper/DataAnomaly/paper.tex
Paper writing: section 'Experiment'

		\subsection{Experiment on Raw Data}
			We first tested Algorithm~\ref{alg:dynamic} on raw data set in order to see how and why the algorithm works. Due to desensitization process, time stamps in raw data set only tell which hour the transaction was committed. Thus, the histogram was drawn by counting hourly volume of each collection. For $\alpha = 0.2$, we select first 30 days as the evidence set of normal collections; day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections. The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate}, \textit{false positive rate} and \textit{accuracy} were recorded.

@@

>>>>

		\subsection{Experiment on Raw Data}
			We first tested Algorithm~\ref{alg:dynamic} on raw data set in order to see whether and why the algorithm works. Due to desensitization process, time stamps in raw data set only tell which hour the transaction was committed. Thus, the histogram was drawn by counting hourly volume of each collection. For $\alpha = 0.2$, we select first 30 days as the evidence set of normal collections; day 21st to 30th were also emulated to be click farmed, composing the evidence set of anomalous collections. Equation(\ref{equ:sqrt-log-add-weight}) was employed as the threshold calculator. The results are shown in Table~\ref{tab:result-raw-1st}, where \textit{true positive rate}, \textit{false positive rate} and \textit{accuracy} were recorded.

@@

			\textbf{How did we get the result?}

			\begin{table}[!ht]
				\centering
				\caption{1st Level}
				\label{tab:syn-result-1st}
				\begin{tabular}{|c|c|c|c|c|c|c|}
					\hline
					& \multicolumn{3}{c|}{Centralized} & \multicolumn{3}{c|}{Equalized}\\
					\hline
					$\alpha$ & TPR(\%) & FPR(\%) & ACC(\%) & TPR(\%) & FPR(\%) & ACC(\%) \\ 
					\hline
					0.1 & 86.10 & 1.14 & 97.40 & 5.75 & 12.28 & 79.66 \\ 
					\hline
					0.2 & 96.43 & 9.83 & 91.30 & 26.97 & 26.47 & 64.29 \\ 
					\hline
					0.3 & 97.95 & 16.49 & 87.68 & 37.46 & 39.46 & 53.67 \\ 
					\hline
					0.4 & 99.18 & 31.94 & 81.30 & 57.23 & 48.32 & 53.79 \\ 
					\hline
					0.5 & 99.33 & 23.40 & 88.25 & 67.67 & 58.23 & 54.46 \\ 
					\hline
					0.6 & 99.62 & 25.70 & 89.83 & 67.03 & 73.78 & 51.64 \\ 
					\hline
					0.7 & 100.00 & 32.51 & 90.51 & 69.69 & 76.28 & 56.16 \\ 
					\hline
					0.8 & 99.72 & 26.97 & 94.35 & 75.56 & 69.44 & 67.00 \\ 
					\hline
					0.9 & 99.63 & 15.73 & 98.19 & 76.59 & 75.18 & 70.73\\
					\hline
				\end{tabular} 
			\end{table}

			\begin{table}[!ht]
				\centering
				\caption{2nd Level}
				\label{tab:syn-result-2nd}
				\begin{tabular}{|c|c|c|c|c|c|c|}
					\hline
					& \multicolumn{3}{c|}{Centralized} & \multicolumn{3}{c|}{Equalized}\\
					\hline
					$\alpha$ & TPR(\%) & FPR(\%) & ACC(\%) & TPR(\%) & FPR(\%) & ACC(\%) \\ 
					\hline
					0.1 & 75.60 & 3.90 & 93.74 & 97.84 & 1.64 & 98..31 \\ 
					\hline
					0.2 & 91.93 & 18.43 & 93.73 & 99.42 & 7.39 & 94.01 \\ 
					\hline
					0.3 & 95.01 & 23.70 & 81.69 & 100.00 & 23.93 & 83.05 \\ 
					\hline
					0.4 & 98.09 & 28.66 & 82.49 & 100.00 & 24.59 & 84.75 \\ 
					\hline
					0.5 & 98.33 & 36.54 & 80.00 & 100.00 & 23.76 & 88.36 \\ 
					\hline
					0.6 & 98.35 & 40.69 & 83.41 & 100.00 & 35.94 & 84.63 \\ 
					\hline
					0.7 & 98.54 & 37.97 & 87.80 & 100.00 & 31.27 & 90.84 \\ 
					\hline
					0.8 & 98.47 & 40.38 & 91.19 & 100.00 & 33.04 & 92.66 \\ 
					\hline
					0.9 & 98.51 & 47.56 & 94.58 & 100.00 & 28.44 & 97.40\\
					\hline
				\end{tabular} 
			\end{table}

			\textbf{Comment on the result. Explain the trend:(1)$\alpha \uparrow, TPR \uparrow $; (2)$\alpha \uparrow, FPR \uparrow$; (3)$\alpha \uparrow, ACC \downarrow then \uparrow $}
